|

### 2020-02-25 article/article.Rmd
fix a few typos

We use the TDP app to conduct two experimental interventions and test the
impact of citizen oversight on five outcomes related to school completion rates
and complaints to public authorities. Overall, providing information to
citizens has no consistent impact on policy outcomes. In the first experiment,
we find that the TDP app increased the likelihood of construction cancellation
by 2 per cent, but the result does not replicate. The remaining five models
have null results. In our second intervention, none of the estimations reach
conventional levels of statistical significance. Importantly, all coefficients
are small, what suggests that even if the TDP app had a significant effect on
the outcomes, its substantive impact would be negligible.

@@

Transparência Brazil built the app in from January to March 2017 and tested it
in May of that year. The first stable Android version was deployed on Google
Play on 14 August 2017. A version for iOS came about six months later. In
October 2017, Transparência Brazil started a Facebook campaign in order to
publicise the app. Facebook is the most widely used social media network in
Brazil with around 72 million users [@statista2019facebook]. The campaigns
attracted 2,028 new users to the platform in October 2017 only.

@@

The TDP also received feedback from Brazilian computer scientists and policy
analists. In 2017 and 2018, Transparência Brasil announced two team programming
competitions, called 'Tá de Pé Hackathons', where contributors could fix code
bugs and suggest new functionalities to the TDP project. One of these
innovations consists of a Twitter bot (<https://twitter.com/tadepeapp>) which
posts a message on the social network each time a user submits a new picture
for evaluation or a municipality responds to a citizen's request. This allows
any interested parties, including those who do not use the TDP app, to check
the state of school construction sites.

@@

The second intervention is similar to intervention 1 in all but three
characteristics. First, the TDP app was then available for both Android and iOS
devices. Second, we randomised the intervention at the school level, with 
`r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and 
`r format(as.numeric(table(impact_evaluation_phase2$treat)[2]), big.mark = ",",
scientific = FALSE)` treatment units. We used blocked randomisation stratified
by Brazilian states, school construction status (under construction, stopped,
unfinished), and whether the municipality spent more on school construction
that the distribution median. Finally, the intervention period lasted from
August 2018 to July 2019.

@@

We find that the app only has a small effect on cancellation rates. The TDP
application increases the likelihood of cancelling the construction in 
`r round(100*resInt1[[2]][[20]]$coefficients[1], 2)` percent. While this result
goes in the opposite direction of our theoretical expectations, the finding is
inconsistent and does not replicate in the second experiment. All other
coefficients are not statistically significant at conventional levels. On the
one hand, the results indicate that our placebo outcome, the percentage of the
invested executed before the intervention, indeed behaves as predicted. On the
other hand, we expected the five remaining outcomes to improve after the
introduction of the app. The literature on bottom-up accountability argues that
delivering more information about the shortcomings of public services provision
will put citizens in a position where they can monitor state agents and improve
provider behaviour [@raffler2018weakness]. Our results do not lend support to
that hypothesis.

Table \ref{tab:results2} shows the results of the second intervention. The
treatment does not have a statistically significant effect on any our outcomes
of interest, including the placebo. This raises further questions about the
effect of the TDP app on school completion. Note that the effect signs are also
inconsistent with improving the outcomes, what demonstrates that our results do
not derive from low statistical power or the reduced control group size.

>>>>

We use the TDP app to conduct two experimental interventions and test the
impact of citizen oversight on five outcomes related to school completion rates
and complaints to public authorities. Overall, providing information to
citizens has no consistent impact on policy outcomes. In the first experiment,
we find that the TDP app increased the likelihood of construction cancellation
by 2 per cent, but the result does not replicate. The remaining five models
have null results. In our second intervention, none of the estimations reach
conventional levels of statistical significance. Importantly, all coefficients
are small, which suggests that even if the TDP app had a significant effect on
the outcomes, its substantive impact would be negligible.

@@

Transparência Brazil built the app from January to March 2017 and tested it
in May of that year. The first stable Android version was deployed on Google
Play on 14 August 2017. A version for iOS came about six months later. In
October 2017, Transparência Brazil started a Facebook campaign in order to
publicise the app. Facebook is the most widely used social media network in
Brazil with around 72 million users [@statista2019facebook]. The campaigns
attracted 2,028 new users to the platform in October 2017 only.

@@

The TDP also received feedback from Brazilian computer scientists and policy
analysts. In 2017 and 2018, Transparência Brasil announced two team programming
competitions, called 'Tá de Pé Hackathons', where contributors could fix code
bugs and suggest new functionalities to the TDP project. One of these
innovations consists of a Twitter bot (<https://twitter.com/tadepeapp>) which
posts a message on the social network each time a user submits a new picture
for evaluation or a municipality responds to a citizen's request. This allows
any interested parties, including those who do not use the TDP app, to check
the state of school construction sites.

@@

The second intervention is similar to intervention 1 in all but three
characteristics. First, the TDP app was then available for both Android and iOS
devices. Second, we randomised the intervention at the school level, with 
`r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and 
`r format(as.numeric(table(impact_evaluation_phase2$treat)[2]), big.mark = ",",
scientific = FALSE)` treatment units. We used blocked randomisation stratified
by Brazilian states, school construction status (under construction, stopped,
unfinished), and whether the municipality spent more on school construction
than the distribution median. Finally, the intervention period lasted from
August 2018 to July 2019.

@@

We find that the app only has a small effect on cancellation rates. The TDP
application increases the likelihood of cancelling the construction by `r
round(100*resInt1[[2]][[20]]$coefficients[1], 2)` percent. While this result
goes in the opposite direction of our theoretical expectations, the finding is
inconsistent and does not replicate in the second experiment. All other
coefficients are not statistically significant at conventional levels. On the
one hand, the results indicate that our placebo outcome, the percentage of the
invested executed before the intervention, indeed behaves as predicted. On the
other hand, we expected the five remaining outcomes to improve after the
introduction of the app. The literature on bottom-up accountability argues that
delivering more information about the shortcomings of public services provision
will put citizens in a position where they can monitor state agents and improve
provider behaviour [@raffler2018weakness]. Our results do not lend support to
that hypothesis.

Table \ref{tab:results2} shows the results of the second intervention. The
treatment does not have a statistically significant effect on any of our
outcomes of interest, including the placebo. This raises further questions
about the effect of the TDP app on school completion. Note that the effect
signs are also inconsistent with improving the outcomes, which demonstrates
that our results do not derive from low statistical power or the reduced
control group size.
